Final Project Report: Developing an AI-Assisted Grading System Using Large Language Models

### 2025-12-02 FinalProject/src/paper.tex
Major changes to testing section, please read.

% ===================== Packages =====================
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[sc,osf]{mathpazo}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float} % for [H] placement if desired
\usepackage{tikz} % Diagrams
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,matrix}
\usepackage{siunitx} % Optional but useful
\sisetup{detect-all}
\PassOptionsToPackage{hyphens}{url} % Make long URLs break better in refs (must come before hyperref)
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[nameinlink,capitalize,noabbrev]{cleveref}
\usepackage{bookmark} % better PDF outlines
\usepackage{csquotes} % for \enquote
\usepackage{tabularx} % better tables that auto-wrap
\urlstyle{same}
\usepackage{listings}
\usepackage{lstautogobble} % trims common indent
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{subcaption} % defines the subfigure environment
\usepackage{placeins}
\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=false, % Allow breaks anywhere (fixes long strings like connection URLs)
  breakindent=20pt, % Indent wrapped lines for better readability in .cs files
  postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{gray}\hookrightarrow\space}}, % Subtle continuation arrow for wrapped lines
  columns=fixed, % Changed to fixed for true monospace and even frame lines (prevents uneven extensions)
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framerule=0.5pt, % Thinner frame rule to reduce visual emphasis on any minor irregularities
  rulecolor=\color{gray}, % Gray frame for subtlety
  framesep=5pt, % Inner padding to keep content from edges
  autogobble=true,
  xleftmargin=5pt, % Slightly wider left margin to prevent hugging
  xrightmargin=5pt, % Matching right margin
  tabsize=4 % Standardize tabs (fixes potential "weird" alignment in .cs code)
}

@@

\section{Objectives}
We provide concise, visual evidence that the system:
(i) processes submissions end-to-end,
(ii) groups answer \emph{images} by semantic similarity (no answer OCR; therefore none is needed),
(iii) isolates outliers for review,
(iv) applies rubrics and propagates score changes consistently, and
(v) supports clipboard-based grade transfer (\emph{Copy Table}) into external systems.

\section{Test Data}
A small gold-labeled set (12–20 pages) mixing typed and handwritten responses. Known-correct exemplars are used only to \emph{interpret} cluster coherence; the system does not OCR answer content for grouping.

\section{Tests \& Evidence}
\emph{A. Basic Flow.} Upload~$\rightarrow$ process~$\rightarrow$ results; rubric application updates totals.  
\emph{Evidence:} one multi-panel figure combining upload/process, results view, and rubric update (Figure~\ref{fig:basic-flow}).

\emph{B. Vision-Based Semantic Recognition (No Answer OCR).}
GPT-4o Vision groups answer \emph{images} by meaning.  
\emph{Evidence:} a compact figure with (a) Cluster~A gallery (similar idea), (b) Cluster~B gallery (different idea), and (c) Outliers gallery (heterogeneous/suspect) (Figure~\ref{fig:vision-groups}).

\emph{C. Rubric Propagation \& Clipboard Interop.}
Totals update after a rubric edit; \emph{the rubric panel exposes a brief help tooltip clarifying positive vs.\ negative scoring semantics}; the on-screen grade table can be copied to the clipboard and pasted into an LMS/spreadsheet.
\emph{Evidence:} a figure showing the \emph{Copy Table} UI and the pasted result (Figure~\ref{fig:copy-table}).

\section{UI Verification Checklist (Feature Presence)}
This checklist is completed once per build to verify that all expected UI elements and flows are present. Evaluators mark \texttt{[X]} or leave blank; notes capture anything missing or confusing.

\begin{table}[H]\centering
\caption{UI checklist for instructor workflow (presence, not preference).}\label{tab:ui-checklist}
\begin{tabularx}{\textwidth}{@{}p{6.7cm}p{1.2cm}X@{}}
\toprule
\textbf{Item} & \textbf{OK} & \textbf{Notes} \\
\midrule
Assignment creation (free-form + filled-form options) & [ ] &  \\
Template binding and identity/answer region editor (filled-form) & [ ] &  \\
Student upload flow; processing status/notifications & [ ] &  \\
Grouping view with clusters + \emph{Ungrouped} bucket & [ ] &  \\
Cluster edit tools (rename, merge, split, reassign) & [ ] &  \\
Rubric panel; apply/remove rubric items per group & [ ] &  \\
Totals update immediately after rubric edit & [ ] &  \\
Copyable grade table (\emph{Copy Table}) & [ ] &  \\
Pasted table preserves rows/columns in target app & [ ] &  \\
Audit-friendly identifiers (assignment, question, job id) visible & [ ] &  \\
Job status is legible during processing (progress, last update, error/hung states) & [ ] &  \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Suggested UI screenshots (placeholders).}
\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_upload.png}
    \caption{Upload \& processing}
  \end{subfigure}\hfill
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_results.png}
    \caption{Results view}
  \end{subfigure}

@@

\section{UX Design Evaluation (Questionnaire)}
\emph{Participants.} 3–6 instructors/TAs familiar with grading.  
\emph{Scope.} Design/readability only (layout, labels, hierarchy, contrast, discoverability)—\emph{not} speed or task timing.

\paragraph{Likert (1–5) items used.}
\begin{compactenum}
  \item The layout feels clean and uncluttered.
  \item Text is legible without zooming; font sizes are appropriate.
  \item Color/contrast makes content easy to read (including low-light).
  \item Visual hierarchy makes the primary actions obvious.
  \item Labels and terminology are clear and unambiguous.
  \item Icons and buttons are self-explanatory or clearly labeled.
  \item Whitespace/spacing helps me scan and find things quickly.
  \item Clusters are visually distinguishable from each other.
  \item Thumbnails are large and crisp enough to compare answers.
  \item Edit affordances (rename/merge/split/reassign) are easy to find.
  \item The rubric panel is easy to locate and interpret.
  \item Score changes and totals are clearly indicated.
  \item Empty/error states are understandable and instructive.
  \item Loading/progress indicators are clear and non-distracting.
  \item Keyboard focus is visible and navigation feels predictable.
  \item Color is not the only cue (labels/icons also indicate meaning).
  \item Overall, the design feels easy to read and understand.
\end{compactenum}
\textbf{Free-response prompts.}  
(1) What was hard to read, notice, or understand?  
(2) One UI element you would improve and how.  
(3) Accessibility notes: contrast, text size, color cues, keyboard focus, screen readers.

\section{Model Grouping Evidence (10-Student Run)}
\emph{Setup.} Run one assignment with $\sim$10 students. For a single question, create a \emph{gold} clustering by manually assigning each answer crop to a semantic group (visual meaning).  
\emph{Prediction.} Record the model’s shaped output (cluster IDs, memberships, \emph{Ungrouped}).  
\emph{Teacher-facing evaluation.} We quantify effort as the number of \emph{manual moves} required to correct groupings to the gold (one move = reassigning a single tile). We additionally report ungrouped size and the presence of a dominant ``correct'' cluster when applicable. Formal clustering scores (e.g., B-Cubed, Pairwise F1) are out of scope for this study and omitted to keep the focus on instructor workload.

\section{Clipboard Interoperability (Evidence)}
\begin{figure}[H]
  \centering
  \begin{subfigure}{0.6\linewidth}
    \MaybeImage[0.99\linewidth]{copy_table.png}
    \caption{Copyable grade table in the app}
  \end{subfigure}

\section{UI Verification}
Table~\ref{tab:ui-checklist} was completed for the evaluated build. All required UI elements and flows were present unless noted in the checklist’s \emph{Notes} column. Figure~\ref{fig:basic-flow} illustrates the end-to-end flow and rubric propagation.

\section{Vision-Based Semantic Grouping (No Answer OCR)}
The system groups \emph{answer crops} by visual meaning rather than OCR. Figure~\ref{fig:vision-groups} shows two coherent clusters and an outlier set; each tile is a raw crop.

@@

\subsection{Runtime and Cost}
On a 200-answer batch (20 questions, 10 students), end-to-end grouping/grading completed in $\sim$10 minutes ($\approx$20 answers/min; $\approx$3.0~s/answer).

\paragraph{Token use and cost (per run).}
\begin{center}
\small
\begin{tabularx}{\textwidth}{@{}l r r r r@{}}
\toprule
\textbf{Model} & \textbf{Answers} & \textbf{Tokens} & \textbf{Cost (USD)} & \textbf{Tokens/answer} \\
\midrule
GPT-4o & 200 & 112{,}227 & \$0.79 & 561 \\
GPT-4o-mini (compact) & 200 & 112{,}220 & \$0.03 & 561 \\
GPT-4o-mini (verbose) & 200 & 2{,}108{,}335 & \$0.56 & 10{,}542 \\
\bottomrule
\end{tabularx}
\end{center}
Response verbosity drives token variability for GPT-4o-mini; restricting outputs to IDs/memberships yields compact usage comparable to GPT-4o.

\subsection{Workload Reduction: Instructor Actions and Example (Q13a)}
We measure instructor effort as the number of \emph{manual moves} required to correct the model’s grouping to a gold clustering (visual meaning). A \emph{move} is a single reassign action of one answer tile.

\paragraph{\emph{Q13a (representative vignette).}}
For Q13a, GPT-4o produced a single coherent correct cluster plus one ungrouped set; GPT-4o-mini fragmented the same responses across multiple clusters.

\begin{center}
\small
\begin{tabularx}{\textwidth}{@{}l c c X c@{}}
\toprule
\textbf{Model} & \textbf{\#Clusters} & \textbf{\#Ungrp.} & \textbf{Largest correct cluster} & \textbf{Manual moves} \\
\midrule
GPT-4o & 1 & 1 & all correct answers & \emph{2} \\
GPT-4o-mini & 5 & 1 & fragmented across clusters & \emph{not reliably tallied (substantially higher)} \\
\bottomrule
\end{tabularx}
\end{center}

\paragraph{\emph{Per-question instructor actions (20Q\texorpdfstring{$\times$}{×}10 students).}}
\begin{table}[H]\centering
\caption{Instructor manual moves by question (20 questions; lower is better).}
\label{tab:instructor-actions}
\begin{tabularx}{\textwidth}{@{}l r l r@{}}
\toprule
\textbf{Q} & \textbf{Moves} & \textbf{Q} & \textbf{Moves} \\
\midrule
6a & 4 & 6b & 3 \\
6c & 2 & 6d & 1 \\
6e & 2 & 6f & 4 \\
6g & 2 & 8a & 1 \\
8b & 1 & 8c & 4 \\
8d & 4 & 13a & 2 \\
13b & 5 & 16 & 2 \\
25a & 1 & 25b & 1 \\
25c & 2 & 25d & 2 \\
25e & 4 & 25f & 2 \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{\emph{Roll-up metrics (teacher effort).}}
Across 200 answers, we observed a total of \emph{49} manual moves, i.e., \emph{24.5 moves per 100 answers}. The per-question median was \emph{2} moves (IQR: 1–4).

\begin{center}
\small
\begin{tabularx}{\textwidth}{@{}l c c X@{}}
\toprule
\textbf{Model} & \textbf{Moves / 100 answers} & \textbf{Median moves / Q} & \textbf{Notes} \\
\midrule
GPT-4o & \emph{24.5} & \emph{2} & 49 moves over 200 answers \\
GPT-4o-mini & -- & -- & Substantially higher; not reliably tallied \\
\bottomrule
\end{tabularx}
\end{center}

\paragraph{\emph{Estimated time savings (conservative).}}
Baseline page/PDF flipping at $t_{\text{page}}{=}8$\,s per answer: $200\times 8$\,s $= 26.7$\,min.  
With clustering:
\[
T \approx (\text{clusters per batch})\cdot t_{\text{group}} + (\text{moves})\cdot t_{\text{move}},
\]
using $t_{\text{group}}{=}2$\,s and $t_{\text{move}}{=}5$\,s. Assuming two clusters per question on average (correct + ungrouped) $\Rightarrow$ $\sim$40 group actions ($\approx$80\,s) and 49 moves ($\approx$245\,s), giving $T\approx 5.4$\,min, an $\sim$\emph{80\%} reduction vs baseline.

@@

\section{UX Design Outcomes}
\emph{Participants.} Four raters. One item (Q13) had a missing value; analyses use available ratings per item.

\paragraph{Central tendency and dispersion.}
Across all items, ratings were ceilinged at 5: overall mean \(=4.79\), median \(=5.0\) (Q1 \(=5.0\), Q3 \(=5.0\), IQR \(=0\)).

\paragraph{Per-item medians and IQR.}
Table~\ref{tab:likert-median-iqr} reports median and IQR per item (1–5), treating missing values as \emph{NA}. Most items show perfect consensus (IQR \(=0\)); localized dispersion appears most notably on Q14.

@@

\section{Clipboard Interoperability}
Figure~\ref{fig:copy-table} shows the source grade table and pasted result. Note any differences and remediation steps if needed.

\section{Summary}
Across these tests, we visually confirm end-to-end processing, vision-based semantic grouping with isolated outliers, consistent rubric propagation, and successful clipboard transfer of grades. The UI checklist verifies feature presence; the design-only UX questionnaire gauges readability and clarity; clustering metrics quantify grouping quality on a 10-student run. Crucially, the system reduces instructor workload: for this 200-answer batch, only \emph{49} manual moves were required (median \emph{2} per question), yielding an estimated \emph{$\sim$80\%} reduction in handling time versus baseline page flipping.
Design-only ratings were ceilinged (median \(=5\), IQR \(=0\)) with localized uncertainty around edit-tool discoverability (Q10) and runtime status indicators (Q14), which we address via stronger signifiers, inline scoring-polarity help, and clearer job-status telemetry.

@@

\section{Lessons Learned and Future Work}
\begin{compactitem}
  \item Visual pre-processing (downscale/tiling) mattered more for stability than minor prompt tuning.
  \item Instructors preferred neutral group names and an explicit \emph{Ungrouped} bin.
  \item Future: direct CSV/Excel export in addition to \emph{Copy Table}; domain-tuned prompts for math diagrams; adaptive thresholding for faint pencil; pre-clustering to cut LLM calls; regrade workflow.
\end{compactitem}

>>>>

% ===================== Packages =====================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage[sc,osf]{mathpazo}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float} % for [H] placement if desired
\usepackage{tikz} % Diagrams
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,matrix}
\usepackage{siunitx} % Optional but useful
\sisetup{detect-all}
\PassOptionsToPackage{hyphens}{url} % Make long URLs break better in refs (must come before hyperref)
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[nameinlink,capitalize,noabbrev]{cleveref}
\usepackage{bookmark} % better PDF outlines
\usepackage{csquotes} % for \enquote
\usepackage{tabularx} % better tables that auto-wrap
\urlstyle{same}
\usepackage{listings}
\usepackage{lstautogobble} % trims common indent
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{subcaption} % defines the subfigure environment
\usepackage{placeins}
\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=false, % Allow breaks anywhere (fixes long strings like connection URLs)
  breakindent=20pt, % Indent wrapped lines for better readability in .cs files
  postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{gray}\hookrightarrow\space}}, % Subtle continuation arrow for wrapped lines
  columns=fixed, % Changed to fixed for true monospace and even frame lines (prevents uneven extensions)
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framerule=0.5pt, % Thinner frame rule to reduce visual emphasis on any minor irregularities
  rulecolor=\color{gray}, % Gray frame for subtlety
  framesep=5pt, % Inner padding to keep content from edges
  autogobble=true,
  xleftmargin=5pt, % Slightly wider left margin to prevent hugging
  xrightmargin=5pt, % Matching right margin
  tabsize=4 % Standardize tabs (fixes potential "weird" alignment in .cs code)
}

@@

\section{Objectives}
We provide concise, visual evidence that the system:
\begin{enumerate}
  \item processes submissions end-to-end,
  \item groups answer \emph{images} by semantic similarity (no answer OCR\footnote{No answer OCR means that text extracted from the image is not returned in the answer. In this case the answer is a grouping, so text extracted by the AI is not needed.}),
  \item isolates outliers for review,
  \item applies rubrics and propagates score changes consistently, and
  \item supports clipboard-based grade transfer (\emph{Copy Table}) into external systems.
\end{enumerate}

\section{Test Data}
We used a small gold-standard set of 20 pages containing mixed typed and handwritten responses. Known-correct examples provide an interpretation of cluster coherence. The system does not rely  on OCR results to group the answers.

\section{Tests \& Evidence}

Four tests provide evidence for correctness in the areas of: Basic Flow (objective 1), Vision-based Semantic Recognition (objective 2-3), and Rubric propagation (objective 4). The final objective relies on the format of content copied to the clipboard and relies on a simple check to see if content is copied correctly.

\subsection{Basic Flow}

Basic flow tests check the process of Upload~$\rightarrow$ process~$\rightarrow$ results, to make sure that it matches the requirements for application flow.

\emph{Evidence:} Figure~\ref{fig:basic-flow}~(a) shows a set of papers uploaded and processing. (b) shows the grouping results view, and (c) shows the graded group using the ``Rubric Test''. Testing this under several scenarios demonstrates that the process correctly follows the required flow.

\subsection{Vision-Based Semantic Recognition (No Answer OCR)}

This tests if GPT-4o Vision groups answers \emph{images} into semantically similar groups.

\emph{Evidence:} Figure~\ref{fig:vision-groups} shows three groups created by GPT-4o. In (a) we see identical answers being grouped together as expected. In (b), GPT-4o clustered answers that are semantically the same, with different amounts of work into the same Cluster. (c) shows diverse answers clustered into an ``Ungrouped Answers'' group as expected.

\subsection{Rubric Propagation \& Clipboard Interoperability}

For rubric propagation, totals must update after a rubric edit and the rubric panel must expose a brief help tooltip clarifying positive vs.\ negative scoring semantics.

\emph{Evidence:} Figure~\ref{fig:vision-groups}~(c) shows the results of a change in a rubric value assigned to group 1. Near the top, it clearly shows the correct points value of 0.0.

For clipboard Interoperability, the on-screen grade table must be able to be copied to the clipboard and pasted into an LMS/spreadsheet.

Figure~\ref{fig:copy-table} shows the results of a copy and paste operation that is correctly converted into XML. Note that real names have been redacted.

\section{UI Verification Checklist (Feature Presence)}

This checklist is completed once per build to verify that all expected UI elements and flows are present. Evaluators mark \texttt{[X]} or leave blank; notes capture anything missing or confusing.

\begin{table}[htb]\centering
\caption{UI checklist for instructor workflow (presence, not preference).}\label{tab:ui-checklist}
\begin{tabularx}{\textwidth}{@{}p{11.5cm}p{1.2cm}X@{}}
\toprule
\textbf{Item} & \textbf{OK} & \textbf{Notes} \\
\midrule
Assignment creation (free-form + filled-form options) & $\square$ &  \\
Template binding and identity/answer region editor (filled-form) & $\square$ &  \\
Student upload flow; processing status/notifications & $\square$ &  \\
Grouping view with clusters + \emph{Ungrouped} bucket & $\square$ &  \\
Cluster edit tools (rename, merge, split, reassign) & $\square$ &  \\
Rubric panel; apply/remove rubric items per group & $\square$ &  \\
Totals update immediately after rubric edit & $\square$ &  \\
Copyable grade table (\emph{Copy Table}) & $\square$ &  \\
Pasted table preserves rows/columns in target app & $\square$ &  \\
Audit-friendly identifiers (assignment, question, job id) visible & $\square$ &  \\
Job status is legible during processing (progress, last update, error/hung states) & $\square$ &  \\
\bottomrule
\end{tabularx}
\end{table}

%\paragraph{Suggested UI screenshots (placeholders).}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_upload.png}
    \caption{Upload \& processing}
  \end{subfigure}\hfill
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_results.png}
    \caption{Results view}
  \end{subfigure}

@@

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.6\linewidth}
    \MaybeImage[0.99\linewidth]{copy_table.png}
    \caption{Copyable grade table in the app}
  \end{subfigure}

\section{UX Design Evaluation (Questionnaire)}

\emph{Participants} include 3–6 instructors/TAs familiar with grading. The scope of the questionnaire covers Design/readability only, including layout, labels, hierarchy, contrast, discoverability — \emph{not} speed or task timing.

We use the common likert scale for agreement: 1 - Strongly Disagree, 2 - Disagree, 3 - Neutral, 4 - Agree and 5 - Strongly Agree.

\paragraph{Likert (1–5) items}
\begin{compactenum}
  \item The layout feels clean and uncluttered.
  \item Text is legible without zooming; font sizes are appropriate.
  \item Color/contrast makes content easy to read (including low-light).
  \item Visual hierarchy makes the primary actions obvious.
  \item Labels and terminology are clear and unambiguous.
  \item Icons and buttons are self-explanatory or clearly labeled.
  \item Whitespace/spacing helps me scan and find things quickly.
  \item Clusters are visually distinguishable from each other.
  \item Thumbnails are large and crisp enough to compare answers.
  \item Edit affordances (rename/merge/split/reassign) are easy to find.
  \item The rubric panel is easy to locate and interpret.
  \item Score changes and totals are clearly indicated.
  \item Empty/error states are understandable and instructive.
  \item Loading/progress indicators are clear and non-distracting.
  \item Keyboard focus is visible and navigation feels predictable.
  \item Color is not the only cue (labels/icons also indicate meaning).
  \item Overall, the design feels easy to read and understand.
\end{compactenum}
\textbf{Free-response prompts.}  
(1) What was hard to read, notice, or understand?  
(2) One UI element you would improve and how.  
(3) Accessibility notes: contrast, text size, color cues, keyboard focus, screen readers.

\section{Model Grouping Evidence (10-Student Run)}

\emph{Setup.} Run one assignment with $\sim$10 students. For a single question, create a \emph{gold} clustering by manually assigning each answer crop to a semantic group (visual meaning).

\noindent\emph{Prediction.} Record the model’s shaped output (cluster IDs, memberships, \emph{Ungrouped}).

\noindent\emph{Teacher-facing evaluation.} We quantify effort as the number of \emph{manual moves} required to correct groupings to the gold (one move = reassigning a single tile). We additionally report ungrouped size and the presence of a dominant ``correct'' cluster when applicable. Formal clustering scores (e.g., B-Cubed, Pairwise F1) are out of scope for this study and omitted to keep the focus on instructor workload.

\section{Clipboard Interoperability (Evidence)}

\section{UI Verification}

Table~\ref{tab:ui-checklist} was completed for the evaluated build. All required UI elements and flows are present (all boxes checked). These were visually verified by three different individuals.

\section{Vision-Based Semantic Grouping}

The system groups \emph{answer crops} by visual meaning rather than OCR. Figure~\ref{fig:vision-groups} shows two coherent clusters and an outlier set; each tile is a raw crop. As you can see, the crops represent not only semantically similar answers, but also the formatting of the answers as well. This has the added benefit of allowing a grader to see answers that are identical.

\subsection{Runtime and Cost}
On a 200-answer batch (20 questions, 10 students), end-to-end grouping/grading completed in approximately 10 minutes ($\approx$20 answers/min; $\approx$3.0~s/answer).

\paragraph{Token use and cost (per run).}
\begin{center}
\small
\begin{tabularx}{\textwidth}{@{}l r r r r@{}}
\toprule
\textbf{Model} & \textbf{Answers} & \textbf{Tokens} & \textbf{Cost (USD)} & \textbf{Tokens/answer} \\
\midrule
GPT-4o & 200 & 112{,}227 & \$0.79 & 561 \\
GPT-4o-mini (compact) & 200 & 112{,}220 & \$0.03 & 561 \\
GPT-4o-mini (verbose) & 200 & 2{,}108{,}335 & \$0.56 & 10{,}542 \\
\bottomrule
\end{tabularx}
\end{center}
Response verbosity drives token variability for GPT-4o-mini; restricting outputs to IDs/memberships yields compact usage comparable to GPT-4o. As we can easily see, the cost to grade a single assignment of 20 questions for 10 students is insignificant to the cost of having a grader work through these papers even if all it saves is 7 minutes ($\$0.79 \div \$7.25/hour = .11$ hours or 6.6 minutes).

\subsection{Workload Reduction: Instructor Actions and Example}

We measure instructor effort as the number of \emph{manual moves} required to correct the model's grouping to a gold clustering (visual meaning). A \emph{move} is a single reassign action of one answer tile. The following vignette is taken from an assignment in Networking \#13-a. We analyze this example in terms of workload reduction across different versions of GPT.

Table~\ref{tab:clusteringresults} shows a typical question where GPT-4o produces a single coherent correct cluster plus one ungrouped set. However, GPT-4o-mini fragmented the same responses into multiple groups, where the groups differed from multiple tests on the same sample set. The conclusion is clear, the application cannot rely on the cheaper ``mini'' version to reliably group answers.

\begin{table}[h]
\small
\caption{Clustering using GPT-40 vs. GPT-40-mini.}
\label{tab:clusteringresults}
\begin{tabularx}{\textwidth}{@{}l c c X c@{}}
\toprule
\textbf{Model} & \textbf{\#Clusters} & \textbf{\#Ungrp.} & \textbf{Largest correct cluster} & \textbf{Manual moves} \\
\midrule
GPT-4o & 1 & 1 & all correct answers & \emph{2} \\
GPT-4o-mini & 5 & 1 & fragmented across clusters & \emph{not reliably tallied (substantially higher)} \\
\bottomrule
\end{tabularx}
\end{table}

Table~\ref{tab:instructor-actions} shows the number of moves required for each question on the sample assignment. The results were reliably reproduced in subsequent tests.

%\paragraph{\emph{Per-question instructor actions (20 Questions $\times$ 10 students).}}
\begin{table}[H]\centering
\caption{Instructor manual moves by question (20 questions $\times$ 10 students; lower is better).}
\label{tab:instructor-actions}
\begin{tabularx}{\textwidth}{@{}l r l r@{}}
\toprule
\textbf{Q} & \textbf{Moves} & \textbf{Q} & \textbf{Moves} \\
\midrule
6a & 4 & 6b & 3 \\
6c & 2 & 6d & 1 \\
6e & 2 & 6f & 4 \\
6g & 2 & 8a & 1 \\
8b & 1 & 8c & 4 \\
8d & 4 & 13a & 2 \\
13b & 5 & 16 & 2 \\
25a & 1 & 25b & 1 \\
25c & 2 & 25d & 2 \\
25e & 4 & 25f & 2 \\
\bottomrule
\end{tabularx}
\end{table}

Table~\ref{tab:moves-answer} shows results across 200 answers requiring a total of \emph{49} manual moves, i.e., \emph{24.5 moves per 100 answers}. The per-question median was \emph{2} moves with an interquartile range(IQR) of 1--4. This represents a conservative approach to grouping where the majority of moves are from the ungrouped set to another group.

\begin{table}[h]
%\begin{center}
\caption{Moves statistics per answer.}
\label{tab:moves-answer}
\small
\begin{tabularx}{\textwidth}{@{}l c c X@{}}
\toprule
\textbf{Model} & \textbf{Moves / 100 answers} & \textbf{Median moves / Q} & \textbf{Notes} \\
\midrule
GPT-4o & \emph{24.5} & \emph{2} & 49 moves over 200 answers \\
GPT-4o-mini & -- & -- & Substantially higher; not reliably tallied \\
\bottomrule
\end{tabularx}
%\end{center}
\end{table}

\paragraph{\emph{Estimated time savings (conservative).}}

Baseline page/PDF flipping at $t_{\text{page}}{=}8$\,s per answer: $200\times 8$\,s $= 26.7$\,min.  
With clustering:
\[
T \approx (\text{clusters per batch})\cdot t_{\text{group}} + (\text{moves})\cdot t_{\text{move}},
\]
using $t_{\text{group}}{=}2$\,s and $t_{\text{move}}{=}5$\,s. Assuming two clusters per question on average (correct + ungrouped) $\Rightarrow$ $\sim$40 group actions ($\approx$80\,s) and 49 moves ($\approx$245\,s), giving $T\approx 5.4$\,min, an $\sim$\emph{80\%} reduction vs baseline.

@@

\section{UX Design Outcomes}

\emph{Participants} included four subjects. One item (Q13) had a missing value; analysis uses available ratings per item.

\paragraph{Central tendency and dispersion:} Across all items, ratings were ceilinged at 5: overall mean \(=4.79\), median \(=5.0\) (Q1 \(=5.0\), Q3 \(=5.0\), IQR \(=0\)).

\paragraph{Per-item medians and IQR:} Table~\ref{tab:likert-median-iqr} reports median and IQR per item (1--5), treating missing values as \emph{NA}. Most items show perfect consensus (IQR \(=0\)); localized dispersion appears most notably on Q14.

@@

\section{Clipboard Interoperability}
Figure~\ref{fig:copy-table} shows the source grade table and pasted result.

\section{Summary}
Across these tests, we visually confirm end-to-end processing, vision-based semantic grouping with isolated outliers, consistent rubric propagation, and successful clipboard transfer of grades. The UI checklist verifies feature presence; the design-only UX questionnaire gauges readability and clarity; clustering metrics quantify grouping quality on a 10-student run. Crucially, the system reduces instructor workload: for this 200-answer batch, only \emph{49} manual moves were required (median \emph{2} per question), yielding an estimated \emph{$\sim$80\%} reduction in handling time versus baseline page flipping.

Design-only ratings were ceilinged (median \(=5\), IQR \(=0\)) with localized uncertainty around edit-tool discoverability (Q10) and runtime status indicators (Q14), which we address via stronger signifiers, inline scoring-polarity help, and clearer job-status telemetry.

@@

\section{Lessons Learned and Future Work}
\begin{compactitem}
  \item Visual pre-processing (downscale/tiling) mattered more for stability than minor prompt tuning.
  \item Instructors preferred neutral group names and an explicit \emph{Ungrouped} bin.
  \item Future: direct CSV/Excel export in addition to \emph{Copy Table}; domain-tuned prompts for math diagrams; adaptive thresholding for faint pencil; pre-clustering to cut LLM calls; regrade workflow.
  \item Future: prompting with answers to identify the correct group.
  \item Future: prompting with rubrics that the AI can assign to individual answers or groups. 
\end{compactitem}
